QPLIB: A Library of Quadratic Programming Instances

### 2018-02-02 QPLIB-2.2.tex
Update QPLIB-2.2.tex

>>>>

\textcolor{red}{
Furthermore, as previously remarked, a not (positive or negative) definite $Q^i$ does not necessarily correspond to a nonconvex feasible region. For instance, it is well-known that Second-Order Cone Programs have convex feasible regions; when represented in terms of quadratic constraints, however, they correspond to $Q^i$ in one negative eigenvalue. In our taxonomy we still consider the corresponding instances as $**Q$ ones, with no attempt to detect the different special structures that actually correspond to convex feasible regions. Although this may lead to classify as ``potentially nonconvex'' some instances that are in fact convex, our choice is justified by the fact that not all QP solvers are capable of detecting and exploiting these structures, which means that the instance can actually be treated as a nonconvex one even if it is not.
}
